---
title: "hlp01"
author: "pma"
date: "September 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# HLP

```{r}

library(tidytext)
library(tm)
library(e1071)
library(odbc)


```


```{r}

hpl01 <- read_csv("hpl01.csv")

# colnames(hpl01) <- c("year", "n", "title")

hpl02 <- hpl01 %>% group_by(year) %>% mutate(max(n))

hpl03 <- hpl02[,c(1,5)] %>% unique()
colnames(hpl03) <- c("year", "n")
hpl03$n <- hpl03$n %>% as.numeric()
hpl03 <- hpl03 %>% rbind( c(year=1929, n=0)) # 1929 had zero 

hpl03 <- hpl03[order(hpl03$year),]

slack_years <- (min(hpl03$year):max(hpl03$year)) %>% setdiff(hpl03$year)

plot(hpl03$n~hpl03$year,type='l')
points(hpl03$year, hpl03$n )

```

```{r}

hpl <- function() {
  result <- new.env(emptyenv())
  
  get_titles_per_year_ <- function(it)  it  %>% group_by(year) %>% mutate(max(n))
  get_characters_per_year_ <- function(it)  it %>% group_by(year) %>% mutate(sum(length))
  
  do_the_thing <- function(fn) {

    hpl01 <- read_csv("hpl01.csv")
    hpl02 <- hpl01 %>% fn()
    hpl03 <- hpl02[,c(1,5)] %>% unique()
    colnames(hpl03) <- c("year", "n")
    hpl03$n <- hpl03$n %>% as.numeric()
    hpl03 <- hpl03 %>% rbind( c(year=1929, n=0)) # 1929 had zero 
    hpl03 <- hpl03[order(hpl03$year),]
    hpl03
    
  }

  
    result$get_titles_per_year <- function() {
     do_the_thing(get_titles_per_year_)
  }
  
  result$get_characters_per_year <- function() {
    
     do_the_thing(get_characters_per_year_)    
  }
  
  result$both <- function(){
    
    r2 <- result$get_titles_per_year() %>% left_join(  result$get_characters_per_year(), "year")
    colnames(r2) <- c("year", "titles", "characters")
    r2
  }
  
  result
  
}


x0 <- hpl()

x1 <- x0$both()
x1 <- x1%>%mutate(q=characters/titles)


```




```{r}


fn <- function(the_formula, the_parameter) {
  plot(the_formula, main=paste("Lovecraft's", the_parameter, "over Time"), xlab="year", ylab=the_parameter)
  hm <- lm(the_formula)
  abline(hm)
}

fn(x1$titles~x1$year, "Titles per Year")
fn(x1$characters~x1$year, "Characters Written")
fn(x1$q~x1$year, "Characters per Title")





```




```{r}

#barplot((x1$characters+1) %>% log(), names.arg = x1$year)
#barplot(x1$titles, names.arg = x1$year)

#11.9


ch01 <- (x1$characters+1) %>% log()

ch02 <- ch01 %>% stats::kmeans(5)

mypalette<-brewer.pal(5,"RdBu")
barplot((x1$characters+1) %>% log(), names.arg = x1$year, col= mypalette[ch02$cluster])



```




```{r}

barplot(x1$titles, names.arg = x1$year,col= mypalette[ch02$cluster], main="Lovecraft Stories per Year"   )

legend("topright", c("none", "<2k", "<20k", "<50k", ">50k"), fill=mypalette%>%rev(), title="Words Per Year")

```







```{r}

hpl01 <- read_csv("hpl01.csv")

# colnames(hpl01) <- c("year", "n", "title")

hpl02 <- hpl01 %>% group_by(year) %>% mutate(sum(length))

hpl03 <- hpl02[,c(1,5)] %>% unique()
colnames(hpl03) <- c("year", "n")
hpl03$n <- hpl03$n %>% as.numeric()
hpl03 <- hpl03 %>% rbind( c(year=1929, n=0)) # 1929 had zero 

hpl03 <- hpl03[order(hpl03$year),]

slack_years <- (min(hpl03$year):max(hpl03$year)) %>% setdiff(hpl03$year)

plot(hpl03$n~hpl03$year,type='l')

```


```{sh}

ls -l txt

```





```{r}


x1 <- VCorpus(DirSource("txt"))


x1 <- x1 %>%tm_map(removePunctuation) 
 x1 <- tm_map(x1, removeWords, stopwords("english")) 
# x1 <- x1 %>% tm_map(anti_join(stopwords("english"))
dtm0 <- x1  %>% DocumentTermMatrix()
q0 <- dtm0 %>% tidy() 
q0 <- q0[ order(q0$count, decreasing=TRUE), ]
q0

```


```{r}

x2 <- x1 %>% tidy()

x3 <- x2 %>% unnest_tokens(word,text) %>% anti_join(stop_words)


q3 <- x3 %>% count(word) %>% group_by(word) 


q3 <- q3[ order(q3$n, decreasing = TRUE), ]

plot( q3$n)
```


```{r}


hpl01 %>% group_by()

```







# Ken

Hi Ken,

Glad you're back!  Hope the vacation was great -- did you go anywhere good?

Feel free to let us know if there is anything we should add to the list of countermeasures.  In particular, how do we plan on ensuring better focus at the next hack?
Let Clarie know if you think of any other ideas for the next hack.
You can look at the list of next steps for us.  If you get time, you may want to see if you can connect to the AWS database.  Ramin was able to do so when we met and I think this will be a good way to coordinate sanitized data at the next hack.
I am trying to use ML concepts to address the question of which USIT projects are 'similar'.  Not getting very far with that -- any help or advice would be appreciated as well.

Really sorry that you couldn't make it when we met; hopefully it was worth it to keep 'momentum' going.  We felt that we should at least try to meet the week before the next hack, either on Wednesday the 9th or Friday the 11th.  Let us know what you think (and if you can make your office available :-) ).  Do you think there will be a way to meet between then and now?  Maybe even if just virtually?  Let us know what you think and what days might be good.

referenced docs:
https://github.com/possibly-sam/mcfc02/tree/master/docs



# Prasad

Thanks Prasad,

It's great to hear that everything should be fully ready to go on the 3rd, I am very excited for it. 

I have received a description of the offer from HR, and was told that they would send the remainder of the details shortly.  Do you know when I might expect these further details?
 
Otherwise, see you on the 3rd about 10:00!
 


## Hello Phillip,

Sorry didn't come back yesterday as I was touching base with hr to ensure all was in line with your start. This morning they have confirmed that you are all good to start on 3rd and not aware of anything waiting on your end to complete.

Have a good break and see you on the 3rd. Aim to be in office around 10am and as usual ask for me at reception.

Thanks,
Prasad

Get Outlook for Android





